Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-24 products/manuscript/Manuscript.qmd
prj2

**Figure 4 : Comparative Discriminative Performance of ML Models for Predicting Adverse Birth Outcomes**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
roc_lr  <- roc_curve(logistic_preds, truth = adverse_birth_outcome, .pred_1) %>% mutate(model = "Logistic")
roc_rf  <- roc_curve(rf_preds,       truth = adverse_birth_outcome, .pred_1) %>% mutate(model = "RF")
roc_xgb <- roc_curve(xgb_preds,     truth = adverse_birth_outcome, .pred_1) %>% mutate(model = "XGBoost")

roc_all <- bind_rows(roc_lr, roc_rf, roc_xgb)

ggplot(roc_all, aes(x = 1 - specificity, y = sensitivity, color = model)) +
  geom_path(size = 1) +
  labs(title = "",
       x = "False Positive Rate", y = "True Positive Rate") +
  theme_minimal()
```

>>>>

**Figure 4 : Comparative Discriminative Performance of ML Models for Predicting Adverse Birth Outcomes**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  here::here(
    "Images",
    "Figure 4.Comparative Discriminative Performance of ML .png"
  )
)
